%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work/Social Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	\cventry
	{Member} % Job title
	{Institution for Hajj and Umroh} % Organization
	{South Sulawesi, Indonesia} % Location
	{2022 - 2027} % Date(s)
	{}
	\cventry
	{Lecturer} % Job title
	{Muhammadiyah Univerisity of Parepare} % Organization
	{South Sulawesi, Indonesia} % Location
	{2022 Oct 19  - Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item{Teaching city and regional planning course and other courses according to specialization and department needs}
			\item{Pursuing research}
			\item {Making/grading test and homework.}
			\item{Keeping student records.}
		\end{cvitems}
	}
	\cventry
	{Drafter} % Job title
	{Sahabat Karya Sejati} % Organization
	{Central Java, Indonesia} % Location
	{2021 Mar - 2021 Sep} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Drafted as built drawings for 10 junior high school renovations.}
			\item{Wrote daily reports of each 10 project of renovations.}
			\item{Occasionally supervised each 10 projects which is located spread across Ngawi Regency.}
		\end{cvitems}
	}
	\cventry
	{Volunteer} % Job title
	{PAMIY (A group of Architecture Student of Yogyakarta)} % Organization
	{Yogyakarta, Indonesia} % Location
	{2017 Apr} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Constructed a simple bookcase for library in a Mosque of Parangritis village }
			\item{Cleaned up the area around the mosque}
		\end{cvitems}
	}
	\cventry
	{Assistant lecturer of DED course} % Job title
	{University Technology of Yogyakarta} % Organization
	{Yogyakarta, Indonesia} % Location
	{2016-2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Prepared all computer to be used for Detail Engineering Drawing (DED) practices and gave an overview of the lessons of the day.}
			\item{Mentored students who had difficulty on understanding the lessons.}
			\item{Handed a homework to student regarding the lessons.}
		\end{cvitems}
	}
	\cventry
	{Participant of Archimony Competition} % Job title
	{PAMIY} % Organization
	{Yogyakarta, Indonesia} % Location
	{2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item{Participated in all preparation of the event about one month.}
			\item {Worked as security and consumption division.}
		\end{cvitems}
	}
\end{cventries}
